\LARGE \bf My Paper Title

### 2016-12-11 paper.tex
Generating bibliography from citations used in paper

% Set the title.
\title{\LARGE \bf Your Awesome Title Here}

@@

% New section.
\section{Introduction}

% New section.
\section{Details}

% New sub-section.
\subsection{Figures}

@@

% A figure.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{figures/mountains.jpg}
\caption{Majestic mountains.}
\label{fig:mountains}
\end{figure}

% New sub-section.
\subsection{Bullets}

@@

% New sub-section.
\subsection{Equations}

@@

% New sub-section.
\subsection{Figures}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

\begin{table}[h]
\caption{An Example of a Table}
\label{table_example}
\begin{center}
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{center}
\end{table}

% New sub-section.
\subsection{Tables}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

\begin{figure}[thpb]
\centering
\framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
}}
%\includegraphics[scale=1.0]{figurefile}
\caption{Inductance of oscillation winding on amorphous
magnetic core versus DC bias magnetic field}
\label{figurelabel}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader. As an example, write the quantity Magnetization, or Magnetization, M, not just M. If including units in the label, present them within parentheses. Do not label axes only with units. In the example, write Magnetization (A/m) or Magnetization {A[m(1)]}, not just A/m. Do not label axes with a ratio of quantities and units. For example, write Temperature (K), not Temperature/K.

\section{Conclusion}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

\section*{Appendix}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

\section*{Acknowledgment}

@@

% Start of the bibliography.
\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.

\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.

\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.

\bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.

\bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.

% End of the bibliography.
\end{thebibliography}

>>>>

% The package for the bibliography.
\usepackage{biblatex}

% The name of the bibliography file.
\addbibresource{source/references.bib}

% Set the title.
\title{\LARGE \bf My Paper Title}

@@

% New section.
\section{Introduction}
\label{sec:introduction}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
\cite{knuthwebsite}
All work and no play makes Jack a dull boy.

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

% New section.
\section{Details}
\label{sec:details}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

% New sub-section.
\subsection{Figures}
\label{sec:details_figures}

@@

% A figure.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth,natwidth=400,natheight=300]{figures/mountains.jpg}
\caption{Majestic mountains.}
\label{fig:mountains}
\end{figure}

% New sub-section.
\subsection{Bullets}
\label{sec:details_bullets}

@@

% New sub-section.
\subsection{Equations}
\label{sec:details_equations}

@@

% New sub-section.
\subsection{Tables}
\label{sec:details_tables}

@@

\begin{table}[h]
\caption{An Example of a Table}
\label{tab:table_a}
\begin{center}
\begin{tabular}{|c||c|c|}
\hline
One & Two & Three\\
\hline
Four & Five & Six\\
\hline
\end{tabular}
\end{center}
\end{table}

\section{Conclusion}
\label{sec:conclusions}

% New sub-section.
\subsection{Important Stuff}
\label{sec:conclusions_important_stuff}

\section*{Appendix}
\label{sec:appendix}

\section*{Acknowledgment}
\label{sec:acknowledgment}

% Generate the bibliography.
\printbibliography

% % Start of the bibliography.
% \begin{thebibliography}{99}

% \bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.

% \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.

% \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.

% \bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.

% \bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.

% % End of the bibliography.
% \end{thebibliography}
